Computing the bicharacter of huge subspaces of polynomials

### 2019-04-30 article/article.tex
Add polarization and steenrod op.

	Note that $\Delta:=$ $\prod_{i<j}(x_i-x_j)$ is harmonic and that if $f$ is harmonic then $\partial_i f$ is also harmonic. \\

@@

	%define polarization operators

>>>>

	Note that $V_n:=$ $\prod_{i<j}(x_i-x_j)$ is harmonic and that if $f$ is harmonic then $\partial_i f$ is also harmonic. \\

@@

	\begin{definition}
		The \emph{polarisation operator} $P_{x_a,x_b}^k$ is given by
		$$P_{x_a,x_b}^k = \sum_{i=1}^{n} x_{bi} \partial_{x_{ai}}^k$$
		where $x_a$ and $x_b$ are two sets of variables of $X$. 
	\end{definition}

	It is well known (\cite{Haiman2002} and \cite{Bergeron2009}) that the harmonics $\harmonics_{n,1}$ are generated by the Vandermonde determinant $V_n$ and closed by partial derivatives. Moreover, the diagonal harmonics $\harmonics_{n,r}$ are generated by $\harmonics_{n,1}$ and closed by the polarization operators.

	\begin{definition} \pauline{how to introduce them ?}
		The \emph{Steenrod operator} $St_{x_a}^k$ for $k>1$ is given by
		$$St_{x_a}^k = \sum_{i=1}^{n} x_{ai} \partial_{x_{ai}}^k$$
		where $x_a$ is a set of variables of $X$. 
	\end{definition}

	Only the Steenrod operators for $k=2$ and $k=3$ are necessary since the other operators can be obtained from the two first ones. For example, $St_{x_a}^4 = St_{x_a}^3St_{x_a}^2 - St_{x_a}^2St_{x_a}^3$.

	Note that $St_{x_a}^k = P_{x_a,x_a}^k$ but we distinguish the two families of operators because they play different roles.
